### 2019-11-21 report/02-methods.Rmd
Test stab div in different context: basin, consistence of biomass trajectories

@@

$$
C_k = CV_{-k} - CV
$$

@@

>>>>

### Community

Community composition were analyzed thanks to [NMDS](https://jonlefcheck.net/2012/10/24/nmds-tutorial-in-r/).

```{r}
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(community_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload(habitat_pressure, dir = mypath("report"))
```

```{r}
com <- ungroup(community_analysis) %>%
  select(opcod, species, biomass) %>%
  spread(species, biomass) %>%
  left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
  mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
  select(-opcod) %>%
  group_by(station) %>%
  summarise_all(list(median))

com_mat <- as.matrix(com[, names(com) != "station"]) 
```

```{r}
library(vegan)

nmds <- metaMDS(com_mat, k=3, trymax = 100)

stressplot(nmds)
plot(nmds)
ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="gray",air=0.01)
```

```{r}
# Add habitat
match_st <- match(habitat_pressure$station, com$station)
habitat <- habitat_pressure[order(match_st), ]
match_st_com <- match(temporal_community_metrics$station, com$station)
com_metrics <- temporal_community_metrics[order(match_st_com), ]

ordisurf(nmds,habitat$alt,main="",col="forestgreen")
```

```{r}

hab_var <- c("temperature", "alt", "lat", "flow", "width_river_mean", "DBO")
par(mfrow = c(2,3))
for (i in seq_along(hab_var)) {
  ordisurf(nmds, habitat[[hab_var[i]]], main = hab_var[i], col = "brown")
}

```{r}
com_var <- c("richness_med", "biomass_stab", "biomass_med")
par(mfrow = c(2,2))
for (i in seq_along(com_var)) {
  ordisurf(nmds, com_metrics[[com_var[i]]], main = com_var[i], col =
    "forestgreen")
}
```

```{r basin-st}
station_analysis <- get_basin_station(sf_obj = TRUE)
plot(station_analysis[,"basin"])
# How many station by basin:
nb_st_basin <- station_analysis %>%
  group_by(basin) %>%
  summarise(nobs = n())
```

```{r basin-com}
match_st_basin <- match(station_analysis$station, com$station)
st_basin <- station_analysis[order(match_st_basin), ]

ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="red",air=0.01)
ordihull(nmds, groups = st_basin[["basin"]], draw="polygon",col="grey90",label=F)
```

@@

$$
C_{k} = CV_{-k} - CV
$$

@@

### Time series classification

```{r load dataset, include = FALSE}
library(jmotif)
myload(community_metrics, op_analysis, dir = mypath("data"))
community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
```

```{r}
ts_biomass  <- community_metrics %>%
  select(station, date, biomass) %>%
  mutate(station = as.character(station)) %>%
  group_by(station) %>%
  arrange(date) %>%
  nest()

ts_biomass %<>%
  mutate(
    zts = map(data, function(x) znorm(x$biomass, threshold = 0.01)),
    paa = map(zts, ~paa(., 3)),
    sax = map_chr(paa, ~series_to_string(., 3))
  )

biomass_ts_sax <- ts_biomass 
mysave(biomass_ts_sax, dir = mypath("data"), overwrite = TRUE)
```

```{r}
pattern_dist <- ts_biomass %>%
  group_by(sax) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
ggplot(ts_biomass, aes(x = sax)) +
  geom_histogram(stat = "count")
```

```{r}
test <- ts_biomass %>%
  filter(sax %in% c("cba", "bbb", "cab", "abc", "acb", "bca", "bac", "cbb")) %>%
  group_by(sax) %>%
  sample_n(10) %>%
  mutate(
    paa2 = map2(data, zts, function (x, zts) {
      cbind(x[,1], zts)
  }),
    id_sta = as.character(seq(1,n()))

  ) %>%
  unnest(paa2)

ggplot(test, aes(x = date, y = zts)) +
  geom_line(aes(color = id_sta)) +
  facet_wrap(~ sax)

```{r}
myload(polluant_units, dir = mypath("data-raw", "polluants", "naiades_data"))

myload(press_metrics, dir = mypath("data"))
press_year <- press_metrics %>%
  filter(category %in% c("fungicides", "herbicides", "insecticides", "DBO", "temperature"))

biomass <- community_metrics %>%
  mutate(
    year = lubridate::year(date),
    category = "biomass",
    press = biomass 
    ) %>%
  select(station, year, category, press)
press_biomass <- press_year %>%
  bind_rows(rename(biomass, id = station)) %>%
  na.omit()
```

```{r}
samp_station <- sample(unique(press_biomass$id), 10)
temp <- press_biomass %>%
  mutate(id = as.character(id)) %>%
  filter(id %in% samp_station)

ggplot(temp, aes(y = press, x = year)) +
  facet_wrap(~category, scales = "free_y") +
  geom_line(aes(color = id))

### 2019-11-21 report/05-stability.Rmd
Test stab div in different context: basin, consistence of biomass trajectories

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "local_network_build.R"))
```
```{r}
temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) 
%>%
  select(station, troph_group, biomass_cv, richness_avg, nbnode_med) %>%
  gather(richness_type, div, richness_avg, nbnode_med) %>%
  ggplot(aes(x = div, y = biomass_cv, color = troph_group)) +
  facet_grid(cols = vars(richness_type), scales = "free_x") +
  geom_point() +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    )
```

@@

One missing part was the fact that we do not know the assembly rules of the
trophic group.

@@

cv_bm_div_troph_grp %>%
  ggplot(aes(y = cv_st, x = div_st)) +
  geom_point() +
  facet_grid(cols = vars(troph_group))
```

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
```
```{r}
st_basin <- get_basin_station() 
myload(region_polygon, dir = mypath("data"))
stab_div_basin <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  select(station, troph_group, biomass_stab, richness_avg) %>%
  left_join(st_basin, by = "station") %>%
  filter(!is.na(basin))

# By basin
p_stab_div_basin <- ggplot(stab_div_basin,
  aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
  facet_wrap(~basin, ncol = 4) +
  geom_point() +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
  )
# Total
p_stab_div_tot <-  ggplot(stab_div_basin,
  aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
  geom_point() +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
  )

plot_grid(p_stab_div_basin, p_stab_div_tot, nrow = 2)

```{r}
myload(biomass_ts_sax, dir = mypath("data"))
p_bbb_stab_div <- stab_div_basin %>%
  mutate(station = as.character(station)) %>%
  left_join(biomass_ts_sax[, c("station", "sax")], by = "station") %>%
  filter(sax == "bbb") %>%
  ggplot(aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
  geom_point() +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
  )

station_map <- get_basin_station(sf_obj = TRUE) %>%
  mutate(station = as.character(station)) %>%
  left_join(biomass_ts_sax[, c("station", "sax")], by = "station") %>%
  mutate(type = ifelse(sax == "bbb", "stable", "unstable")) %>%
  select(type)

p_bbb_map <- ggplot(region_polygon) +
  geom_sf() +
  geom_sf(data = station_map, aes(color = type))
#plot(station_map, pch = 16)

plot_grid(p_bbb_stab_div, p_bbb_map, ncol = 2)
```

```{r temp-grp}
myload(habitat_pressure, dir = mypath("report"))

@@

@@
